\maketitle                      %% Mandatory
\begin{abstract}                %% Mandatory -  maximum 350 words
  The \texttt{genthesis.cls} \LaTeX{} class file and accompanying
  documents, such as this sample thesis, are distributed in the hope
  that it will be useful but without any warranty (without even the
  implied warranty of fitness for a particular purpose).  For a
  description of this file's purpose, and instructions on its use, see
  below.

  These files are distributed under the GPL which should be included
  here in the future.  Please let the author know of any changes or
  improvements that should be made.

  Michael Forbes.
  mforbes@physics.ubc.ca
\end{abstract}

\chapter{Preface} % Manditory if any of the conditions are met

You must include a preface if any part of your research was partly or
wholly published in articles, was part of a collaboration, or required
the approval of UBC Research Ethics Boards.

The Preface must include the following:

\begin{itemize}
\item A statement indicating the relative contributions of all
  collaborators and co-authors of publications (if any), emphasizing
  details of your contribution, and stating the proportion of research
  and writing conducted by you.
\item A list of any publications arising from work presented in the
  dissertation, and the chapter(s) in which the work is located.
\item The name of the particular UBC Research Ethics Board, and the
  Certificate Number(s) of the Ethics Certificate(s) obtained, if
  ethics approval was required for the research.
\end{itemize}

%%% Sections and subsections etc. in the Preface should in general
%%% not be listed in the table of contents, so use the starred form
%%% of \section etc.
\section*{Examples}




Note that this preface must come before the table of contents.  Note
also that this section ``Examples'' should not be listed in the table
of contents, so we have used the starred form: \verb|\section*{Example}|.

\tableofcontents                %% Mandatory
\listoftables                   %% Mandatory if thesis has tables
\listoffigures                  %% Mandatory if thesis has figures
\listof{Program}{List of Programs} %% Optional
%% Any other lists should come here, i.e.
%% Abbreviation schemes, definitions, lists of formulae, list of
%% schemes, glossary, list of symbols etc.

\chapter{Acknowledgements}      %% Optional
This is the place to thank professional colleagues and people who have
given you the most help during the course of your graduate work.

\chapter{Dedication} %% Optional
The dedication is usually quite short, and is a personal rather than
an academic recognition.  The \emph{Dedication} does not have to be
titled, but it must appear in the table of contents.  If you want to
skip the chapter title but still enter it into the Table of Contents,
use this command \verb|\chapter[Dedication]{}|.

Note that this section is the last of the preliminary pages (with
lowercase Roman numeral page numbers).  It must be placed
\emph{before} the \verb|\mainmatter| command.  After that, Arabic
numbered pages will begin.

% Any other unusual prefactory material should come here before the
% main body.

% Now regular page numbering begins.
\mainmatter

% Parts are the largest structural units, but are optional.
%\part{Thesis}

% Chapters are the next main unit.
